Moral Foundations of U.S. Political News Organizations

### 2022-03-03 manuscript_version/manuscript_metapsych.Rmd
finally fixed the comma in the tables

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

@@

tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]))

@@

```{r exp1-source-descriptives, results = 'asis', echo = FALSE}
#change this to match
apa_table(as.data.frame(tableprint),
          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula. V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
          caption = "Experiment 1 - Descriptive Statistics by Source", 
          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 10)), 
          font_size = 'footnotesize'
          )
```

@@

@@

tableprint2[ , c(2:6, 8)] = printnum(as.numeric(tableprint2[ , c(2:6, 8)]))
tableprint2[ , 7] = printp(as.numeric(tableprint2[ , 7]))
```

```{r exp1-table, results = 'asis', echo = F}
apa_table(as.data.frame(tableprint2),
          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
          caption = "Experiment 1 Results - Multilevel Model",
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7)),
          font_size = 'footnotesize'
          )
```

@@

  final_kav$valenceavg[i] = mean(tempwords_kav$tempval, na.rm = T)
}
# tapply(final_kav$valenceavg, final_kav$Source, mean)
# tapply(final_kav$valenceavg, final_kav$Source, sd)
# tapply(final_kav$wordcount, final_kav$Source, mean)
# tapply(final_kav$wordcount, final_kav$Source, sd)
# tapply(final_kav$uniquewords, final_kav$Source, mean)
# tapply(final_kav$uniquewords, final_kav$Source, sd)
# tapply(final_kav$Source, final_kav$Source, length)
# tapply(final_kav$wordcount, final_kav$Source, sum)
library(quanteda)
final_kav$FK = NA
for (i in 1:nrow(final_kav)){
  final_kav$FK[i] = unlist(textstat_readability(final_kav$Text[i], 
                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
}
# tapply(final_kav$FK, final_kav$Source, mean)
# tapply(final_kav$FK, final_kav$Source, sd)
#Kav Table
####build the table here####
tableprint3 = matrix(NA, nrow=10, ncol=11)
colnames(tableprint3) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
#tableprint3[ , 1] = unique(final_kav$Source)
tableprint3[ , 1] = c("The Blaze", "Breitbart", "Fox News", "Sean Hannity", 
                     "Huffington Post", "NPR", "New York Times", "Politico",
                     "Rush Limbaugh", "Slate")
tableprint3[ , 2] = tapply(final_kav$valenceavg, final_kav$Source, mean, na.rm = T)
tableprint3[ , 3] = tapply(final_kav$valenceavg, final_kav$Source, sd, na.rm = T)
tableprint3[ , 4] = tapply(final_kav$valenceavg, final_kav$Source, length)
tableprint3[ , 5] = tapply(final_kav$wordcount, final_kav$Source, sum, na.rm = T)
tableprint3[ , 6] = tapply(final_kav$wordcount, final_kav$Source, mean, na.rm = T)
tableprint3[ , 7] = tapply(final_kav$wordcount, final_kav$Source, sd)
tableprint3[ , 8] = tapply(final_kav$uniquewords, final_kav$Source, mean, na.rm = T)
tableprint3[ , 9] = tapply(final_kav$uniquewords, final_kav$Source, sd, na.rm = T)
tableprint3[ , 10] = tapply(final_kav$FK, final_kav$Source, mean, na.rm = T)
tableprint3[ , 11] = tapply(final_kav$FK, final_kav$Source, sd, na.rm = T)
tableprint3[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint3[ , c(2,3,6,7,8,9,10,11)]))
tableprint3 = tableprint3[c(5, 6, 7, 8, 10, 1, 2, 3, 4, 9), ]
```

```{r exp2-source-descriptives-kav, results = 'asis', echo = FALSE, message = F}
#change this to match
apa_table(as.data.frame(tableprint3),
          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula. V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
          caption = "Kavanaugh - Descriptive Statistics by Source", 
          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 10)),
          font_size = 'footnotesize'
          )
```

@@

tableprint4[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint4[ , c(2,3,6,7,8,9,10,11)]))

@@

```{r exp2-source-descriptives-gs, results = 'asis', echo = FALSE, message = F}
#change this to match
apa_table(as.data.frame(tableprint4),
          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula. V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
          caption = "Government Shutdown - Descriptive Statistics by Source", 
          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 10)),
          font_size = 'footnotesize'
          )
```

@@

For news articles about the partial U.S. Federal Government Shutdown of 2018-2019, there were no significant or practical effects of political lean for the moral foundations. A small-to-medium effect size was observed for *authority/respect*. The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources. This effect was similar to Experiment 1 in which the largest effect size was observed for *authority/respect*. As noted before, the effect found in Experiment 1 was in the opposite direction as what was hypothesized. Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size. Owing to a lack of similar effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for *authority/respect*.

@@

tableprint_kav[ , c(2:6, 8)] = printnum(as.numeric(tableprint_kav[ , c(2:6, 8)]))
tableprint_kav[ , 7] = printp(as.numeric(tableprint_kav[ , 7]))
```

```{r exp2-tablekav, results = 'asis', echo = F}
apa_table(as.data.frame(tableprint_kav),
          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
          caption = "Kavanaugh Results - Multilevel Model", 
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7)),
          font_size = 'footnotesize'
          )
```

@@

tableprint_gs[ , c(2:6, 8)] = printnum(as.numeric(tableprint_gs[ , c(2:6, 8)]))
tableprint_gs[ , 7] = printp(as.numeric(tableprint_gs[ , 7]))
```

```{r exp2-tablegs, results = 'asis', echo = F}
apa_table(as.data.frame(tableprint_gs),
          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
          caption = "Government Shutdown Results - Multilevel Model", 
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7)),
          font_size = 'footnotesize'
          )
```

>>>>

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

@@

tableprint[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint[ , c(2,3,6,7,8,9,10,11)]), big.mark = "")

@@

@@

```{r exp1-source-descriptives, results = 'asis', echo = FALSE}
#change this to match
apa_table(as.data.frame(tableprint),
          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula. V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
          caption = "Experiment 1 - Descriptive Statistics by Source", 
          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 10)), 
          font_size = 'footnotesize',
          placement = "h"
          )
```

@@

tableprint2[ , c(2:6, 8)] = printnum(as.numeric(tableprint2[ , c(2:6, 8)]), big.mark = "")
tableprint2[ , 7] = printp(as.numeric(tableprint2[ , 7]))
```

```{r exp1-table, results = 'asis', echo = F}
apa_table(as.data.frame(tableprint2),
          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
          caption = "Experiment 1 Results - Multilevel Model",
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7)),
          font_size = 'footnotesize',
          placement = "h"
          )
```

@@

  final_kav$valenceavg[i] = mean(tempwords_kav$tempval, na.rm = T)
}
# tapply(final_kav$valenceavg, final_kav$Source, mean)
# tapply(final_kav$valenceavg, final_kav$Source, sd)
# tapply(final_kav$wordcount, final_kav$Source, mean)
# tapply(final_kav$wordcount, final_kav$Source, sd)
# tapply(final_kav$uniquewords, final_kav$Source, mean)
# tapply(final_kav$uniquewords, final_kav$Source, sd)
# tapply(final_kav$Source, final_kav$Source, length)
# tapply(final_kav$wordcount, final_kav$Source, sum)
library(quanteda)
final_kav$FK = NA
for (i in 1:nrow(final_kav)){
  final_kav$FK[i] = unlist(textstat_readability(final_kav$Text[i], 
                     measure = "Flesch.Kincaid")$Flesch.Kincaid)
}
# tapply(final_kav$FK, final_kav$Source, mean)
# tapply(final_kav$FK, final_kav$Source, sd)
#Kav Table
####build the table here####
tableprint3 = matrix(NA, nrow=10, ncol=11)
colnames(tableprint3) = c("Source", "Mean_Valence", "SD_Valence", "Number_of_Articles", "Total_Words", "Mean_Tokens", "SD_Tokens", "Mean_Types", "SD_Types", "Mean_Readability", "SD_Readability")
#tableprint3[ , 1] = unique(final_kav$Source)
tableprint3[ , 1] = c("The Blaze", "Breitbart", "Fox News", "Sean Hannity", 
                     "Huffington Post", "NPR", "New York Times", "Politico",
                     "Rush Limbaugh", "Slate")
tableprint3[ , 2] = tapply(final_kav$valenceavg, final_kav$Source, mean, na.rm = T)
tableprint3[ , 3] = tapply(final_kav$valenceavg, final_kav$Source, sd, na.rm = T)
tableprint3[ , 4] = tapply(final_kav$valenceavg, final_kav$Source, length)
tableprint3[ , 5] = tapply(final_kav$wordcount, final_kav$Source, sum, na.rm = T)
tableprint3[ , 6] = tapply(final_kav$wordcount, final_kav$Source, mean, na.rm = T)
tableprint3[ , 7] = tapply(final_kav$wordcount, final_kav$Source, sd)
tableprint3[ , 8] = tapply(final_kav$uniquewords, final_kav$Source, mean, na.rm = T)
tableprint3[ , 9] = tapply(final_kav$uniquewords, final_kav$Source, sd, na.rm = T)
tableprint3[ , 10] = tapply(final_kav$FK, final_kav$Source, mean, na.rm = T)
tableprint3[ , 11] = tapply(final_kav$FK, final_kav$Source, sd, na.rm = T)
tableprint3[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint3[ , c(2,3,6,7,8,9,10,11)]), big.mark = "")
tableprint3 = tableprint3[c(5, 6, 7, 8, 10, 1, 2, 3, 4, 9), ]
```

```{r exp2-source-descriptives-kav, results = 'asis', echo = FALSE, message = F}
#change this to match
apa_table(as.data.frame(tableprint3),
          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula. V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
          caption = "Kavanaugh - Descriptive Statistics by Source", 
          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 10)),
          font_size = 'footnotesize',
          placement = "h"
          )
```

@@

tableprint4[ , c(2,3,6,7,8,9,10,11)] = printnum(as.numeric(tableprint4[ , c(2,3,6,7,8,9,10,11)]), big.mark = "")

@@

```{r exp2-source-descriptives-gs, results = 'asis', echo = FALSE, message = F}
#change this to match
apa_table(as.data.frame(tableprint4),
          note = "Readability statistics were calculated using the Flesch-Kincaid Grade Level readability formula. V = Valence, T = Tokens or total words, Ty = Types or unique words, FK = Flesch-Kincaid",
          caption = "Government Shutdown - Descriptive Statistics by Source", 
          col.names = c("Source", "$M_V$", "$SD_V$", "$N_{Article}$", "$N_{Words}$", "$M_T$", "$SD_T$", "$M_{Ty}$", "$SD_{Ty}$", "$M_{FK}$", "$SD_{FK}$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 10)),
          font_size = 'footnotesize',
          placement = "h"
          )
```

@@

@@

tableprint_kav[ , c(2:6, 8)] = printnum(as.numeric(tableprint_kav[ , c(2:6, 8)]), big.mark = "")
tableprint_kav[ , 7] = printp(as.numeric(tableprint_kav[ , 7]))
```

```{r exp2-tablekav, results = 'asis', echo = F}
apa_table(as.data.frame(tableprint_kav),
          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
          caption = "Kavanaugh Results - Multilevel Model", 
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7)),
          font_size = 'footnotesize',
          placement = "h"
          )
```

For news articles about the partial U.S. Federal Government Shutdown of 2018-2019, there were no significant or practical effects of political lean for the moral foundations (see Table \@ref(tab:exp2-tablegs)). A small-to-medium effect size was observed for *authority/respect*. The effect was in the predicted direction as well, as conservative sources tended to offer more positive endorsements of the foundation than liberal sources. This effect was similar to Experiment 1 in which the largest effect size was observed for *authority/respect*. As noted before, the effect found in Experiment 1 was in the opposite direction as what was hypothesized. Thus, it is difficult to draw comparisons between the two studies despite the similar pattern for effect size. Owing to a lack of similar effects for either Experiment 1 or the Kavanaugh topic, there is doubt as to whether or not a practical or generalized effect exists for *authority/respect*.

@@

tableprint_gs[ , c(2:6, 8)] = printnum(as.numeric(tableprint_gs[ , c(2:6, 8)]), big.mark = "")
tableprint_gs[ , 7] = printp(as.numeric(tableprint_gs[ , 7]))
```

```{r exp2-tablegs, results = 'asis', echo = F}
apa_table(as.data.frame(tableprint_gs),
          note = "For mean and standard deviation values, 'C' and 'L' refer to 'conservative' and 'liberal,' respectively",
          caption = "Government Shutdown Results - Multilevel Model", 
          col.names = c("Foundation", "$M_C$", "$SD_C$", "$M_L$", "$SD_L$", "$t$", "$p$", "$d$"),
          format = "latex",
          escape = F,
          align = c("l", rep("c", 7)),
          font_size = 'footnotesize',
          placement = "h"
          )
```
